Paper Analysis

### 2025-04-11 Paper_WriteUp/Paper_Plots.qmd
making fig4 x-axis same length fr each subplot

```{r figure 4 left}
winner_plot_17_19 <- player_pars |> 
  filter(param == 2) |> 
  mutate(prob = 1/(1 + exp( -1 * value)) - 0.5) |> 
  ggplot(aes(y = reorder(player_name, prob, FUN = median), x = prob)) +
  stat_histinterval() +
  labs(x = "Change in Win Probability", y = element_blank(), 
       title = "1700-1900 Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  theme_single_y()

@@

```{r figure s4 left - plot player effects}
#| eval: false
indiv_plot_17_19 <- player_pars |> 
  filter(param == 1) |> 
  ggplot(aes(y = reorder(player_name, value, FUN = median), x = value)) +
  stat_histinterval() +
  labs(x = "Estimated Player Effect", y = element_blank(),
       title = "1700-1900 Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  theme_single_y()

>>>>

```{r figure 4 left}
winner_plot_17_19 <- player_pars |> 
  filter(param == 2) |> 
  mutate(prob = 1/(1 + exp( -1 * value)) - 0.5) |> 
  ggplot(aes(y = reorder(player_name, prob, FUN = median), x = prob)) +
  stat_histinterval() +
  labs(x = "Change in Win Probability", y = element_blank(), 
       title = "1700-1900 Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  xlim(c(-0.1, 0.1)) +
  theme_single_y()

@@

```{r figure s4 left - plot player effects}
#| eval: false
indiv_plot_17_19 <- player_pars |> 
  filter(param == 1) |> 
  ggplot(aes(y = reorder(player_name, value, FUN = median), x = value)) +
  stat_histinterval() +
  labs(x = "Estimated Player Effect", y = element_blank(),
       title = "1700-1900 Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  xlim(c(-0.1, 0.1)) +
  theme_single_y()
